---
title: "Vignette Title"
author: "Mark J Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Drop cross-reactive probes from `minfi` objects

Use the example data set in `minfiData`, which is 450K array comprising of 3 cancer samples and 3 normal controls.

```{r, load_minfi_data}
suppressPackageStartupMessages(library(minfiData))
data(MsetEx)
MsetEx
```

Call `dropXreactiveLoci` function to remove cross-reactive probes/loci:

```{r, drop_demo}
library(maxprobes)
MsetEx_noXloci <- maxprobes::dropXreactiveLoci(MsetEx)
MsetEx_noXloci
```

The probe/locus number (first number on `dim` row) drops from `r nrow(MsetEx)` to `r nrow(MsetEx_noXloci)`.

## Obtain cross-reactive probe/loci IDs

If you need to get the list of probes/loci (e.g. you do not use `minfi` objects), you can get it by `xreactive_probes` function. It takes an argument `array_type` which is either "EPIC" or "450K", for EPIC/850K and 450K arrays, respectively.

```{r, xloci_demo}
xloci <- maxprobes::xreactive_probes(array_type = "EPIC")
length(xloci)

xloci <- maxprobes::xreactive_probes(array_type = "450K")
length(xloci)
```

